Responses to Review Comments

### 2025-06-24 writeUps/paper.tex
finished first draft of responses

\RequirePackage{amsmath,amsfonts,amssymb,amsthm}
%\RequirePackage[authoryear]{natbib}
\usepackage{longtable}
%\usepackage[notablist,tablesfirst]{endfloat}% To `separate' figures and tables from text if required

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
\usepackage[doublespacing]{setspace}% To produce a `double spaced' document if required
%\setlength\parindent{24pt}% To increase paragraph indentation when line spacing is doubled

@@

Using each simulated dataset, we estimated $\eff0$ and $\eff1$ with three methods: a mixture model \eqref{eq:mixtureModelPS} including principal scores, \textsc{geepers}, and the principal score weighting estimator \eqref{eq:psw}.

@@

The mixture estimator then fits two outcome models:
For the treatment group, the regression model $Y=\beta_0^T+\beta_1^TS+\bm{\gamma}'\bx+\epsilon$ and for the control group, a mixture model of the form \eqref{eq:mixtureModelPS}, but with $\muc0$ and $\muc1$ replaced by regression functions $\beta_0^C+\bm{\gamma}'\bx$ and $\beta_0^C+\beta_1^C+\bm{\gamma}'\bx$, respectively.
Residual variance was allowed to differ across treatment groups, but not across principal strata.
These models were fit simultaneously using Bayesian Markov Chain Monte Carlo with Stan \citep{rstan}, and principal effects $\eff0$ and $\eff1$ estimated as $\beta_0^T-\beta_0^C$ and $\beta_0^T+\beta_1^T-\beta_0^C-\beta_1^T$, respectively. We interpreted the posterior mean as a point estimate and the posterior standard deviation as a standard error.

For \textsc{geepers} and principal score weighting, the principal score model was fit by itself, to data from the treatment group, using standard maximum likelihood methods.
For \textsc{geepers}, we used the estimated principal scores in the control group, along with the observed $S$ in the treatment group, to construct $R$, and then fit the model \eqref{eq:reg2} with OLS.
To estimate standard errors, we computed the sandwich covariance matrix following the procedure detailed in the appendix.

For principal score weighting we plugged estimated principal scores into \eqref{eq:psw} to estimate $\muc0$ and $\muc1$, estimated $\mut0$ and $\mut1$ with the sample means of subjects with $Z=1$ and $S=0$ or $S=1$, respectively, and estimated $\heff0=\hat{\mu}_{Tw}^0-\hat{\mu}_{Cw}^0$ and $\heff1=\hat{\mu}_{Tw}^1-\hat{\mu}_{Cw}^1$.

\subsection{Results}\label{sec:simResults}
In this section, we evaluate estimates of $\eff1$. Results for estimates of $\eff0$ and $\eff1-\eff0$, which are similar, can be found in the online appendix. 
In replication $b=1,\dots,500$, define the error of a given estimator $\heff1_b$ as $err_b=\heff1_b-\eff1$. The bias of $\heff1$, $\EE[\heff1-\eff1]$, is estimated as $\widehat{bias}=\sum_b err_b/500$, and the empirical standard error is defined as $\left\{\sum_b(\heff1_b-\overline{\heff1})^2/499\right\}^{1/2}$, the sample standard deviation of $\heff1$. We also report the empirical coverage of confidence intervals, the proportion of replications in which $\eff1$ is within the estimated confidence bounds of $\heff1$. Here, we present results on error, bias, empirical standard error, and confidence itnterval coverage; results on root-mean-squared-error %$\left(\widehat{bias}^2+SE_{emp}^2\right)^{1/2}$ 
$\left(\sum_b err_b^2/500\right)^{1/2}$
are available in the online appendix.

\subsubsection{Varying $n$ and $\alpha$}
When $\alpha=0$, Assumption \ref{ass:vps} was violated, and \textsc{geepers} estimates were highly erratic; however, as Table \ref{tab:coverage} shows, when other assumptions held, inference remained valid.

@@

\subsubsection{Other Factors}

@@

%<<<<<<< HEAD
Figure \ref{fig:boxplots} shows violin plots, layered on top of jittered scatter plots, showing estimation error for \textsc{geepers}, the parametric mixture model, and the \textsc{psw} estimator of $\eff1$ for, and Table \ref{tab:coverage} shows empirical coverage of nominal 95\% confidence interval estimates for \textsc{geepers} and a parametric mixture models; when at least one of an estimator's assumptions is violated, the result is colored red.

The first row of Table \ref{tab:coverage} and the first column of Figure \ref{fig:boxplots} show similar results as Figure \ref{fig:alphan}---when all assumptions of both methods are met, \textsc{geepers} is slightly less biased than the parametric mixture model; when $\alpha=0.2$, \textsc{geepers} is much more variable and $\alpha=0.5$ the difference in variance is slight.
\textsc{psw} has by far the lowest variance and the highest bias; the latter is due to the violation of principal ignorability.

The remainder of the results reflect violations modeling assumptions for either \geepers or the parametric mixture model or both: interactions in the data generating model between covariates $X$ and treatment assignment $Z$ and/or principal stratum $S$, either of which would violate assumption \ref{ass:rci} and the linear additive model of the \textsc{pmm}, and/or residuals drawn from a uniform distribution, which violates the normality assumption of \textsc{pmm}.
For \geepers, when $\alpha=0.2$ the presence of interactions in the data-generating model increases sampling variance, but only interactions between $X$ and $Z$ reduce confidence interval coverage. When $\alpha=0.5$, the presence of interactions has little to no effect on the performance of the \geepers estimator, and all 95\% confidence intervals approximately achieve their nominal levels. \geepers makes no assumptions about the shape of the residual distribution and behaves similarly under either normal or uniform residuals.

@@

\caption{\label{tab:coverage}Empirical coverage of nominal 95\% confidence intervals for estimates of $\tau^1$.}
\centering
\begin{tabular}[t]{lllllll}
\toprule
\multicolumn{3}{c}{ } & \multicolumn{2}{c}{$\alpha=0.2$} & \multicolumn{2}{c}{$\alpha=0.5$} \\
\cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
\makecell[l]{Residual\\Dist.} & \makecell[l]{X:Z\\Int.?} & \makecell[l]{X:S\\Int.?} & \geepers & \pmm & \geepers & \pmm\\
\midrule
 & No & No & 0.97 & 0.97 & 0.96 & 0.96\\

 & Yes & No & \rd{0.88} & \rd{0.74} & \rd{0.94} & \rd{0.89}\\

 & No & Yes & \rd{0.98} & \rd{0.97} & \rd{0.97} & \rd{0.96}\\

\multirow{-4}{*}{\raggedright\arraybackslash Normal} & Yes & Yes & \rd{0.9} & \rd{0.77} & \rd{0.94} & \rd{0.88}\\
\cmidrule{1-7}
 & No & No & 0.97 & \rd{0.4} & 0.95 & \rd{0.61}\\

 & Yes & No & \rd{0.87} & \rd{0.2} & \rd{0.93} & \rd{0.48}\\

 & No & Yes & \rd{0.98} & \rd{0.53} & \rd{0.96} & \rd{0.57}\\

\multirow{-4}{*}{\raggedright\arraybackslash Uniform} & Yes & Yes & \rd{0.88} & \rd{0.21} & \rd{0.94} & \rd{0.53}\\
\bottomrule
\multicolumn{7}{p{3.5in}}{\footnotesize Based on 500 replications. $n=500$, $\beta_1=0.3$. Simulation standard error $\approx 1$ percentage point. Estimates colored \rd{red} indicate cases where the assumptions of the model are not met.}

\end{tabular}
\end{table}

@@

\subsection{Accounting for Imperfect Compliance: Re-Analysis of the Obstetrics and Periodontal Therapy Study}
Periodontal disease, a weakening of bone and connective tissue supporting teeth, is highly prevalent among American adults and is associated with adverse pregnancy outcomes, including preterm birth \citep{periodontalEpi}.
The Obstetrics and Periodontal Therapy Study \citep[(OPTS)][]{michalowicz2006treatment} investigated the efficacy of nonsurgical periodontal treatment to reduce the preterm birth rate; replication data are available at \url{https://causeweb.org/tshs/obstetrics-and-periodontal-therapy/}.
Pregnant patients at four different hospitals who were at least 16 years old, at less than 16 weeks and 6 days of gestation, and diagnosed with periodontal disease were individually randomized to either receive periodontal treatment during the first 21 weeks of pregnancy ($Z=1$, $n_T=413$) or after delivery ($Z=0$, $n_C=410$).
The primary prespecified outcome of the study was the babies' gestational age at birth; however, the study team also collected data on several secondary birth outcomes, as well as measures of patients' periodontal disease at follow-up.

@@

\subsubsection{Principal Stratification and Alternatives}
The goal of principal strafication in this context is to determine if assignment to the ASSISTments condition affected students who tend to request frequent bottom-out hints differently than students who tended to request fewer bottom-out hints.
Is this the right question to ask?

>>>>

\RequirePackage{amsmath,amsfonts,amssymb,amsthm}
%\RequirePackage[authoryear]{natbib}
\usepackage{longtable}
%\usepackage[notablist,tablesfirst]{endfloat}% To `separate' figures and tables from text if required
\usepackage{threeparttable}
\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
\usepackage[doublespacing]{setspace}% To produce a `double spaced' document if required
%\setlength\parindent{24pt}% To increase paragraph indentation when line spacing is doubled

@@

Using each simulated dataset, we estimated $\eff0$ and $\eff1$ with three methods: \geepers, a parametric mixture model \eqref{eq:mixtureModelPS} including principal scores---hereafter \pmm---and the principal score weighting estimator \eqref{eq:psw}, hereafter \psw.

@@

\pmm, the parametric mixture estimator, then fits two outcome models:
For the treatment group, the regression model $Y=\beta_0^T+\beta_1^TS+\bm{\gamma}'\bx+\epsilon$ and for the control group, a mixture model of the form \eqref{eq:mixtureModelPS}, but with $\muc0$ and $\muc1$ replaced by regression functions $\beta_0^C+\bm{\gamma}'\bx$ and $\beta_0^C+\beta_1^C+\bm{\gamma}'\bx$, respectively.
Residual variance was allowed to differ across treatment groups, but not across principal strata.
These models were fit simultaneously using Bayesian Markov Chain Monte Carlo with Stan \citep{rstan}, and principal effects $\eff0$ and $\eff1$ estimated as $\beta_0^T-\beta_0^C$ and $\beta_0^T+\beta_1^T-\beta_0^C-\beta_1^T$, respectively. We interpreted the posterior mean as a point estimate and the posterior standard deviation as a standard error.

For \textsc{geepers} and \psw, the principal score model was fit by itself, to data from the treatment group, using standard maximum likelihood methods.
For \textsc{geepers}, we used the estimated principal scores in the control group, along with the observed $S$ in the treatment group, to construct $R$, and then fit the model \eqref{eq:reg2} with OLS.
To estimate standard errors, we computed the sandwich covariance matrix following the procedure detailed in the appendix.

For \psw we plugged estimated principal scores into \eqref{eq:psw} to estimate $\muc0$ and $\muc1$, estimated $\mut0$ and $\mut1$ with the sample means of subjects with $Z=1$ and $S=0$ or $S=1$, respectively, and estimated $\heff0=\hat{\mu}_{Tw}^0-\hat{\mu}_{Cw}^0$ and $\heff1=\hat{\mu}_{Tw}^1-\hat{\mu}_{Cw}^1$.

\subsection{Results}\label{sec:simResults}
In this section, we evaluate estimates of $\eff1$. Results for estimates of $\eff0$ and $\eff1-\eff0$, which are similar, can be found in the online appendix. 
In replication $b=1,\dots,500$, define the error of a given estimator $\heff1_b$ as $err_b=\heff1_b-\eff1$. The bias of $\heff1$, $\EE[\heff1-\eff1]$, is estimated as $\widehat{bias}=\sum_b err_b/500$, and the empirical standard error is defined as $\left\{\sum_b(\heff1_b-\overline{\heff1})^2/499\right\}^{1/2}$, the sample standard deviation of $\heff1$. We also report the empirical coverage of confidence intervals, the proportion of replications in which $\eff1$ is within the estimated confidence bounds of $\heff1$. Here, we present results on error, bias, empirical standard error, and confidence interval coverage; results on root-mean-squared-error %$\left(\widehat{bias}^2+SE_{emp}^2\right)^{1/2}$ 
$\left(\sum_b err_b^2/500\right)^{1/2}$
are available in the online appendix.

\subsubsection{Varying $n$ and $\alpha$}
% When $\alpha=0$, Assumption \ref{ass:vps} was violated, and \textsc{geepers} estimates were highly erratic; however, as Table \ref{tab:coverage} shows, when other assumptions held, inference remained valid.
Our first set of results illustrates the performance of \geepers when all of its assumptions are met.
Since \geepers is an asymptotic method whose identification depends on $\bm{x}$ as a predictor of $\st$, we examine its bias and standard error as functions of $n$ and $\alpha$.
We include analogous results for \pmm as a baseline comparison.

@@

\subsubsection{Performance when Assumptions do not Hold}

Our next set of results compares the performance of \geepers, \pmm, and \psw when one or more assumptions of each method may be violated.

@@

%<<<<<<< HEAD
Figure \ref{fig:boxplots} shows violin plots, layered on top of jittered scatter plots, showing estimation error for \geepers, the parametric mixture model \pmm, and the \psw estimator of $\eff1$. Table \ref{tab:coverage} shows empirical coverage of nominal 95\% confidence interval estimates for \geepers and \pmm; when at least one of an estimator's assumptions is violated, the result is colored red.

The first column of Figure \ref{fig:boxplots} and the black entries of Table \ref{tab:coverage} show results from scenarios in which all assumptions of \geepers and \pmm are met (\psw relies on principal ignorability, which is violated throughout the simulation study).
\textsc{geepers} is slightly less biased than the parametric mixture model; when $\alpha=0.2$, \textsc{geepers} is much more variable and $\alpha=0.5$ the difference in variance is slight.
\textsc{psw} has by far the lowest variance and the highest bias; the latter is due to the violation of principal ignorability. 
When all assumptions are met, confidence intervals from both \geepers and \pmm achieve their nominal levels.

The remainder of the results reflect violations modeling assumptions for either \geepers or the parametric mixture model or both: when $\alpha=0$, violating Assumption \ref{ass:vps}; interactions in the data generating model between covariates $X$ and treatment assignment $Z$ and/or principal stratum $S$, either of which would violate assumption \ref{ass:rci} and the linear additive model of the \textsc{pmm}; and/or residuals drawn from a uniform distribution, which violates the normality assumption of \textsc{pmm}.

We omitted the $\alpha=0$ case from Figures \ref{fig:alphan} and \ref{fig:boxplots} since the variance of \geepers and \pmm estimates was so large as to dominate the plot. 
However, the first column of results in Table \ref{tab:coverage} shows that, when other assumptions are met, CIs from both methods tend to over-cover when $\alpha=0$. 
In a randomized experiment, $\alpha$ can be estimated directly, making Assumption \ref{ass:vps} testable.

For \geepers, when $\alpha=0.2$ the presence of interactions in the data-generating model increases sampling variance, but only interactions between $X$ and $Z$ reduce confidence interval coverage. When $\alpha=0.5$, the presence of interactions has little to no effect on the performance of the \geepers estimator, and all 95\% confidence intervals approximately achieve their nominal levels. \geepers makes no assumptions about the shape of the residual distribution and behaves similarly under either normal or uniform residuals.

@@

\caption{\label{tab:coverage}Empirical coverage of nominal 95\% confidence intervals for estimates of $\tau^1$.}
\centering
% \begin{tabular}[t]{lllllll}
% \toprule
% \multicolumn{3}{c}{ } & \multicolumn{2}{c}{$\alpha=0.2$} & \multicolumn{2}{c}{$\alpha=0.5$} \\
% \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
% \makecell[l]{Residual\\Dist.} & \makecell[l]{X:Z\\Int.?} & \makecell[l]{X:S\\Int.?} & \geepers & \pmm & \geepers & \pmm\\
% \midrule
%  & No & No & 0.97 & 0.97 & 0.96 & 0.96\\

%  & Yes & No & \rd{0.88} & \rd{0.74} & \rd{0.94} & \rd{0.89}\\

%  & No & Yes & \rd{0.98} & \rd{0.97} & \rd{0.97} & \rd{0.96}\\

% \multirow{-4}{*}{\raggedright\arraybackslash Normal} & Yes & Yes & \rd{0.9} & \rd{0.77} & \rd{0.94} & \rd{0.88}\\
% \cmidrule{1-7}
%  & No & No & 0.97 & \rd{0.4} & 0.95 & \rd{0.61}\\

%  & Yes & No & \rd{0.87} & \rd{0.2} & \rd{0.93} & \rd{0.48}\\

%  & No & Yes & \rd{0.98} & \rd{0.53} & \rd{0.96} & \rd{0.57}\\

% \multirow{-4}{*}{\raggedright\arraybackslash Uniform} & Yes & Yes & \rd{0.88} & \rd{0.21} & \rd{0.94} & \rd{0.53}\\
% \bottomrule
% \multicolumn{7}{p{3.5in}}{\footnotesize Based on 500 replications. $n=500$, $\beta_1=0.3$. Simulation standard error $\approx 1$ percentage point. Estimates colored \rd{red} indicate cases where the assumptions of the model are not met.}

% \end{tabular}
\input{writeUps/coverageTab}
\end{table}

@@

\subsection{Accounting for Imperfect Compliance: Re-Analysis of the Obstetrics and Periodontal Therapy Study}
\sloppy
Periodontal disease, a weakening of bone and connective tissue supporting teeth, is highly prevalent among American adults and is associated with adverse pregnancy outcomes, including preterm birth \citep{periodontalEpi}.
The Obstetrics and Periodontal Therapy Study \citep[(OPTS)][]{michalowicz2006treatment} investigated the efficacy of nonsurgical periodontal treatment to reduce the preterm birth rate; replication data are available at \url{https://causeweb.org/tshs/obstetrics-and-periodontal-therapy/}.
Pregnant patients at four different hospitals who were at least 16 years old, at less than 16 weeks and 6 days of gestation, and diagnosed with periodontal disease were individually randomized to either receive periodontal treatment during the first 21 weeks of pregnancy ($Z=1$, $n_T=413$) or after delivery ($Z=0$, $n_C=410$).
The primary prespecified outcome of the study was the babies' gestational age at birth; however, the study team also collected data on several secondary birth outcomes, as well as measures of patients' periodontal disease at follow-up.

@@

\subsubsection{Principal Stratification and Alternatives}\label{sec:psInEdTech}
The goal of principal strafication in this context is to determine if assignment to the ASSISTments condition affected students who tend to request frequent bottom-out hints differently than students who tended to request fewer bottom-out hints.
Is this the right question to ask?

### 2025-06-24 writeUps/responses.tex
finished first draft of responses

\usepackage{amsthm}
\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage{bm}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\usepackage{mathtools}
%\usepackage{fullpage}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{numdef}
%\usepackage{multibib}
\usepackage{rotating}

\usepackage[dvipsnames]{xcolor}

@@

@@

\begin{itquote} Given this criterion, it seems to me that the simulation should focus on the last three factors in the design.  That is, I would hold the sample size and alpha fixed.  Currently, too many factors are varied at the same time to give a clear picture.  
I would alter Table 1 to indicate which factors yield assumption violations and then violate these assumptions in isolation instead of relaxing them simultaneously.  As it currently stands, it is quite hard to understand the relative performance of GEEPERs compared to extant methods. Careful relaxation of each assumption allows the reader to see how much bias results from a single factor. 
\end{itquote}
The results in Figure \ref{fig:boxplots} and in Table \ref{tab:coverage} now hold $n$ fixed at $n=500$ per group and completely cross the other factors, i.e. $\alpha=0.2$ or $0.5$, interactions between $\bm{x}$ and $\st$ or $Z$, and the distribution of the residuals.
Now it is apparent from Figure \ref{fig:boxplots} that, for instance, none of the methods are sensitive to interactions between $\bm{x}$ and $\st$, and that \pmm, but not the others, is sensitive to the distribution of the residuals.

In Table \ref{tab:coverage}, results when one or more assumptions have been violated are highlighted in red.

Application.

I thought there were a number of less-than-desirable parts to the application. First, the focus on bottoming out is less than ideal. This strikes me as a fairly rare phenomenon. I didn't find the concept very intuitive and had to read just the descriptive section several times to understand why one might be interested in a principal stratification analysis here.  This makes the methods seem not particularly general.  Why not focus on an application with straightforward one-way noncompliance? This is an area where principal stratification is often applied, and the concepts are well understood.

In addition, it isn't ideal that the ATE in each condition is not estimated very precisely; that is, the CI appears to cover zero in all cases. Next, all the principal stratification estimates are pretty close to the same value as the ATE. That serves as another reason this application isn't compelling. It is hard to care about an application where principal stratification doesn't provide much in the way of insights relative to the ATE. Next, the performance of GEEPERs seems to be quite similar to extant methods in each scenario. Overall, to my thinking, there is little to recommend the current application. Again, there is little here that demonstrates the value of GEEPERs.

To my mind, these problems could both be fixed.  That is, the simulations could be redesigned to provide more compelling evidence. Next, the authors may be able to identify better applications.  Therefore, the manuscript should be revised and resubmitted.

>>>>

\usepackage{amsthm}
\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)
\usepackage{bm}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\usepackage{mathtools}
%\usepackage{fullpage}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{numdef}
%\usepackage{multibib}
\usepackage{rotating}
\usepackage{xspace}
\usepackage[dvipsnames]{xcolor}

@@

We added Section \ref{sec:psInEdTech} to clarify the role principal stratification can play in analyzing implementation data---such as records of which students requested bottom-out hints---from an RCT studying educational effectiveness. 
In that section, we also compared principal stratification to other relevant methods, as you suggested.

@@

\begin{itquote} Given this criterion, it seems to me that the simulation should focus on the last three factors in the design.  That is, I would hold the sample size and alpha fixed.  Currently, too many factors are varied at the same time to give a clear picture.  
I would alter Table 1 to indicate which factors yield assumption violations and then violate these assumptions in isolation instead of relaxing them simultaneously.  As it currently stands, it is quite hard to understand the relative performance of GEEPERs compared to extant methods. Careful relaxation of each assumption allows the reader to see how much bias results from a single factor. 
\end{itquote}
The simulation has two parts: in the first part, we estimate the bias and standard error of \geepers and \pmm for a range of values of $\alpha$ and $n$ when the assumptions of both methods are met.
The goal for the first part is to determine the required sample size and covariate predictability necessary for \geepers to perform well.

The second part presents results for scenarios where assumptions are violated. 
The results in Figure \ref{fig:boxplots} and in Table \ref{tab:coverage} now hold $n$ fixed at $n=500$ per group and completely cross the other factors, i.e. $\alpha=0.2$ or $0.5$, interactions between $\bm{x}$ and $\st$ or $Z$, and the distribution of the residuals.
Now it is apparent from Figure \ref{fig:boxplots} that, for instance, none of the methods are sensitive to interactions between $\bm{x}$ and $\st$, and that \pmm, but not the others, is sensitive to the distribution of the residuals.

Following your fine suggestion, we formatted Table \ref{tab:coverage}, highlighting results in red when one or more assumptions have been violated.
This format makes it clearer that, for instance, \pmm makes distributional assumptions while \geepers does not, and that \geepers is less sensitive to the assumptions that both estimators make, especially when $\alpha=0.5$.

\subsection{Application}
\begin{itquote}
I thought there were a number of less-than-desirable parts to the application. First, the focus on bottoming out is less than ideal. This strikes me as a fairly rare phenomenon. I didn't find the concept very intuitive and had to read just the descriptive section several times to understand why one might be interested in a principal stratification analysis here.  This makes the methods seem not particularly general.  Why not focus on an application with straightforward one-way noncompliance? This is an area where principal stratification is often applied, and the concepts are well understood.

In addition, it isn't ideal that the ATE in each condition is not estimated very precisely; that is, the CI appears to cover zero in all cases. Next, all the principal stratification estimates are pretty close to the same value as the ATE. That serves as another reason this application isn't compelling. It is hard to care about an application where principal stratification doesn't provide much in the way of insights relative to the ATE. Next, the performance of GEEPERs seems to be quite similar to extant methods in each scenario. Overall, to my thinking, there is little to recommend the current application. Again, there is little here that demonstrates the value of GEEPERs.
\end{itquote}

These are important points, which we attempted to address in two ways. 
Most importantly, we included an additional application example, a dental clinical trial with noncompliance, in which \geepers estimated statistically significant principal effects. This example is clean and straightforward, showing an instance where \geepers yields interesting results. 
However, our substantive interests and expertise, as well as those of most of the JREE readership, lie in education research rather than dental science, which prevents us from offering a comprehensive discussion of the method's application or interpreting the \emph{a priori} surprising results.

For that reason, we retained the original application. 
However, we tried to clarify the role PS could play in analyzing student implementation in an RCT studying educational technology. 
For instance, in the Introduction, we wrote ``Indeed, if the use of bottom-out hints is considered part of the treatment, then those students who rarely used them are partial compliers---could the treatment still benefit them?''
Most prominently, we added an extensive discussion in Section \ref{sec:psInEdTech}.
